---
title: "Initial Data Collection, Cleaning, and Analysis"
author: "Jennie Barker"
date: "5/2/2020"
output: html_document
---
## Part 1: In this script, I download, clean, and analyze the initial dataset of interest: Bakke et al (2020)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Collect and Clean Initial Dataset ###
# The initial dataset that I want to analyze is Bakke et al. (2020) "State Restrictions on Civil Society." 

## 1. Load Packages
```{r}
# Remove all objects
rm(list=ls())

# Unload all packages 
library(pacman)
pacman::p_unload(all)

# Add packages 
pacman::p_load(
  tidyverse, 
  data.table,  
  foreign, 
  magrittr, 
  skimr, 
  readxl,
  ggthemes,
  stringr,
  rworldmap
)
```
## 2. Set Working Directory 

```{r}
setwd("~/Documents/Comp Tools - Spring 2020/Final Project ")
getwd()
```

## 3. Load and Examine Dataset 

```{r} 
# Load data - Bakke et al. 2020 - Database on State Restrictions on Civil Society
restrictions_raw <- read_excel("Bakke_dataset.xlsx")

# View data 
restrictions_raw %>% skimr::skim()

# Load raw data as csv file for uploading to the Github repository 
write.csv(restrictions_raw,  file="restrictions_raw.csv")

```


## 4. Subset Dataset
# For the purposes of this project, I am only interested in particular variables in the overall dataset, which includes over 40 variables of 3597 observations. I thus subset the dataset to create a new dataset with only the variables that I want (particularly funding restrictions)

```{r}
# Subset data 
restrictions_subsetted <- select(restrictions_raw, cowcode, COUNTRY, YEAR, ACTIVITIES_RESTRICT, VISIT_RESTRICT, TRAVEL_RESTRICT, FUNDING_INT, FUNDING_DOM, VISAS_DIFFICULTIES, VISAS_DENIED, HARASS_AMOUNT, ARREST, SURVEIL, KILLING, COOPT) 

```


# I am also only interested in recipient countries of democracy assistance, while this dataset includes both donor countries and recipient countries. I thus further subset the dataset. I do this based on members of the DAC minus Eastern European countries, which continue to receive democracy assistance. 
```{r}
# Filter data based on country name and create new data frame 
restrictions_new <- filter(restrictions_subsetted, !COUNTRY %in% c("Australia", "Austria", "Belgium", "Canada", "Denmark", "Finland", "France", "Germany", "Greece", "Iceland", "Ireland", "Italy", "Japan", "Korea, Republic of", "Luxembourg", "Netherlands", "New Zealand", "Norway", "Portugal", "Spain", "Sweden", "Switzerland", "Taiwan", "United Kingdom", "United States of America"))

restrictions_new %>% skimr::skim()
```


## 5. Check Missing Data 
 
```{r}
restrictions_new %<>%
  mutate_if(is.character, list(str_trim))

restrictions_new %>%
  # Keep only character variables 
  select_if(is.character) %>%
  # Recode character variables as 1 if cell is empty 
  mutate_all(list(~ifelse(.=="NA",1,0))) %>%
  # Add up empty cells for each character variable 
  summarise_all(sum, na.rm=T) %>%
  # Transpose data for visibility 
  t() 
```

## 6. Save new data frame 

```{r}
# This will be uploaded to the Github repository 
write.csv(restrictions_new,  file="restrictions_new.csv")
```

## 7. Summary Statistics 

# Before visualizing the initial dataset, I will do some initial summary statistics. This will help me decide what visualizations I want to make. 

```{r}
# First, I will see how many countries had international funding restrictiosn each year using the group_by function and the summarise function 
restrictions_new %>%
  group_by(YEAR) %>%
  summarise(International_Restriction = sum(FUNDING_INT, na.rm=T))
```
## International Funding Restrictions 

```{r}
# Now, I want to see the countries that are behind the international funding restrictions.

# Determine which countries have had at least one yearly instance of international funding restrictions
intlfunding_countries <- restrictions_new %>%
  group_by(COUNTRY) %>%
  filter(sum(FUNDING_INT) >= 1) #this will filter out the countries without this type of restriction 

# Sum of yearly total by country 
intlfunding_country_names <- intlfunding_countries %>%
  group_by(COUNTRY) %>%
  summarise(International_Restriction = sum(FUNDING_INT, na.rm = T))

print(intlfunding_country_names)

# We can now see the countries that have had international funding restrictions in place and how many years they have done so. It appears ~49 countries in total have placed legal restrictions on international funding for NGOs at some point between 1994-2014. 
```

## Visa Denials and Difficulties 

```{r}
# While I am mostly interested in international funding restrictions, I will also check which countries had visa restrictions, as these could affect people working at international organizations that give democracy assistance. 

restrictions_new %>%
  group_by(YEAR) %>%
  summarise(Visa_Restrictions = sum(VISAS_DENIED, na.rm = T))
```

```{r}
# Following a similar script as above: 

# # Determine which countries have had at least one yearly instance of visa denial 
visas_countries <- restrictions_new %>%
  group_by(COUNTRY) %>%
  filter(sum(VISAS_DENIED) >= 1) #this will filter out the countries without this type of restriction 

# Sum of yearly total per country
visas_country_names <- visas_countries %>%
  group_by(COUNTRY) %>%
  summarise(Visa_Denial = sum(VISAS_DENIED, na.rm = T))

print(visas_country_names)

# We can see that many more countries (75) have denied visas at some point than placed restrictions on international funding (49). 

```


```{r}
# Since there are two variables related to visas, I will now look into their combination. 

# Determine which countries have had at least one yearly instance of visa denial or difficulties 
visas_both_countries <- restrictions_new %>%
  group_by(COUNTRY) %>%
  filter(sum(VISAS_DENIED) >= 1 | sum(VISAS_DIFFICULTIES >= 1)) #using the OR function to filter based on both conditions 

# Sum of yearly total per country 
visas_both_country_names <- visas_both_countries %>%
  group_by(COUNTRY) %>%
  summarise(Visa_Denial = sum(VISAS_DENIED), Visa_Difficulty = sum(VISAS_DIFFICULTIES)) #summarise based on two variables 

print(visas_both_country_names)

##There are only 5 additional countries that had visa difficulties without having visa denials. I will only focus on visa denials in the future.  
```
## Cooptation of NGOs 

```{r}
# The third variable I will investigate is the cooptation of NGOs, which indicates if the government sought to bring NGOs under its influence. 

# Determine which countries have had at least one yearly instance of cooptation
coopt_countries <- restrictions_new %>%
  group_by(COUNTRY) %>%
  filter(sum(COOPT) >= 1) #this will filter out the countries without this type of restriction 

# Show sum of year totals per country 
coopt_country_names <- coopt_countries %>%
  group_by(COUNTRY) %>%
  summarise(Cooptation = sum(COOPT, na.rm = T))

print(coopt_country_names)

# This reveals a list of 51 countries that sought to coopt NGOs at some point between 1994-2014. 

```

## Arrests, Harassment, and Killings 

```{r}
# For data visualization purposes, I will also investigate the countries that had arrests, harassment, and killings of members of NGOs. Unlike the previous variables, arrests and harassment are not binary; 0 indicates none, 1 indicates some, and 2 indicates frequent/systematic. 


# Determine which countries have had at least one yearly instance of arrests, harassment, or killings. 
attacks_countries <- restrictions_new %>%
  group_by(COUNTRY) %>%
  filter(sum(ARREST) >= 1 | sum(HARASS_AMOUNT) >= 1 | sum(KILLING) >= 1) #use OR function for three conditions 

# Because two of the variables are not binary, I will group by year. 
attacks_country_names <- attacks_countries %>%
  group_by(COUNTRY, YEAR) %>%
  summarise(Arrest = sum(ARREST, na.rm = T), Harassment = sum(HARASS_AMOUNT, na.rm = T), Killings = sum(KILLING, na.rm = T))

# Show sum of year totals per country 
print(attacks_country_names)

# 123 countries experienced arrest, harassment, or killings. It appears harassment is most common. 

```

```{r}
# Which countries explicitly experienced frequent/systematic harassment or arrests? This will require some mutation from categorical to binary data 

# Mutate existing dataframe and save into a new dataframe
restrictions_new_edited <- restrictions_new %>%
  mutate(ARREST = ifelse(ARREST == "2", 1, 0)) %>% 
  mutate(HARASS_AMOUNT = ifelse(HARASS_AMOUNT == "2", 1, 0))

# Save edited data frame for Github 
write.csv(restrictions_new_edited,  file="restrictions_new_edited.csv")

# Determine which countries have had at least one yearly instance of frequent arrests or harassment
arrests_harass <- restrictions_new_edited %>%
  group_by(COUNTRY) %>%
  filter(sum(ARREST) >= 1 | sum(HARASS_AMOUNT) >= 1)

# Show sum of year totals per country 
arrests_harass_countries <- arrests_harass %>%
  group_by(COUNTRY) %>%
  summarise(Arrest = sum(ARREST, na.rm = T), Harassment = sum(HARASS_AMOUNT, na.rm = T))

print(arrests_harass_countries)

# A total of 78 countries exerpienced either systematic arrests or harassment.

```

## 8. Initial Dataset Visualizations (of key variables)
# The summary statistics above give me a good idea of the initial visualizations I want to do. 

## International Funding Restrictions by Year 
```{r} 
# From above, I have already created relevant dataframes for this visualization: intlfunding_countries and intlfunding_country_names. 

# Because this data is binary, I need to first sum the instances by year 
intl_df <- intlfunding_countries %>% 
  group_by(YEAR) %>%
  summarise(total_intlfunding = sum(FUNDING_INT, na.rm=T))

# Now I will create the line plot 
ggplot (intl_df, aes (x=YEAR, y= total_intlfunding)) +
  geom_line() + #line graph 
  geom_point() + #points at yearly intervals 
  labs( x = "Year", y = "Countries with New Restrictions") + #x and y labels 
  ggtitle("Total Countries with New Restrictions on \n International Funding of NGOs") + #title 
  ylim(0, 25) + #limit for the y-axis 
  theme_economist()+ 
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) + #plot.title centers the title 
  geom_vline(xintercept = 2003, color = "red") #Indication of the Rose Revolution in Georgia 

# Save plot for Github 
ggsave("initialdataset_intlfunding_lineplot.png")
```

# Total Number International Funding Restrictions 

```{r}
# Now I want to visualize the how many years each country had a new international funding restriction. 
intl_df1 <- intlfunding_countries %>% 
  group_by(COUNTRY) %>% #group by country instead of year 
  summarise(total_intlfunding = sum(FUNDING_INT, na.rm=T))

# Now I will create a bar graph 
ggplot(intl_df1, aes(total_intlfunding)) + 
  geom_bar(fill = "steelblue2") + #bar graph 
  labs( x = "Total Number of Years with New Restrictions", y = "Number of Countries") +
  ggtitle("Total Number of Years with International \n Funding Restrictions") +
  theme_economist() +
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) #plot.title centers the title 

# Save plot for Github 
ggsave("initialdataset_intlfunding_barplot_years.png")
```

# Total International Funding Restrictions by Country 
```{r}
# Finally, I want to look at the total number of years with new funding restrictions by country 
intl_df1 <- intlfunding_countries %>% 
  group_by(COUNTRY) %>%
  filter(sum(FUNDING_INT) > 1) %>% #filter out countries without restrictions
  summarise(total_intlfunding = sum(FUNDING_INT, na.rm=T))


# Now I will create a bar graph 
ggplot(intl_df1, aes (x = reorder(COUNTRY, total_intlfunding), y= total_intlfunding)) + #reorder based on number of years 
  geom_bar(stat = "identity", width = 0.5) + #bar graph 
  labs(x = "Country", y = "Total Number of Years") + 
  ggtitle("Countries' Total Number of Years with \n International Funding Restrictions") +
    theme_economist() + 
    theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5, size = 8, margin=margin(-20,0,0,0))) + #Some of the country names are a bit long to fit on the graph, so I'll shorten them.
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) #plot.title centers the title 

# Save plot to upload to Github 
ggsave("initialdataset_intlfunding_barplot_countries.png")
```

# International Funding Restrictions in Comparison with Visa Denials and Cooptation

```{r}
# As noted above, I am only focusing on visa denials instead of both visa denials and difficulties, as there was significant overlap between the two variables. 

intl_visa_coopt_df <- restrictions_new %>%
  group_by(YEAR) %>%
  summarise(total_intlfunding = sum(FUNDING_INT, na.rm = T), total_visas = sum(VISAS_DENIED, na.rm = T), total_coopt = sum(COOPT, na.rm = T)) #include visas in the data frame

# Now to the line plot 

ggplot (intl_visa_coopt_df, aes (x=YEAR)) +
  geom_point(aes(y = total_intlfunding), color = "olivedrab") + #Points on the line 
  geom_point(aes(y = total_visas), color = "deepskyblue1") +
  geom_point(aes(y = total_coopt), color = "gold") +
  geom_line(aes(y = total_intlfunding, color = "olivedrab")) + #Different color lines for each variable 
  geom_line(aes(y = total_visas, color = "deepskyblue1")) +
  geom_line(aes(y = total_coopt, color = "gold")) + 
  labs( x = "Year", y = "Number of Countries") + # labels
  ggtitle("Total Countries with Different Types of \n Restrictions per Year") + #title 
  ylim(0, 30) + 
  theme_economist()+ 
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) + 
  geom_vline(xintercept = 2003, color = "red") + #Indication of the Rose Revolution in Georgia 
  scale_color_identity(name = "Number of Countries", #Legend 
                       breaks = c("olivedrab", "deepskyblue1", "gold"),
                       labels = c("Intl. Funding Restrictions", "Visa Denials",   "Cooptation"),
                       guide = "legend") +
    theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) + #plot.title centers the title 
theme(legend.title = element_text(size = 9), 
               legend.text = element_text(size = 9)) #decrease legend text size 
# Save plot for uploading to Github 
ggsave("initialdataset_intlfunding_visas_cooptation.png")

```

# International Funding Restrictions in Comparison with Frequent/Systematic Harassment 

```{r}
# Finally, I want to plot international funding restrictions with frequent harassment of NGOs using a bubble plot. I already created a binary measure of frequent harassment earlier (line 200)
intl_attack <- restrictions_new_edited %>%
  group_by(YEAR) %>%
  summarise(total_intlfunding = sum(FUNDING_INT, na.rm = T), Harassment = sum(HARASS_AMOUNT, na.rm = T))

#Now to the bubble plot  

ggplot(intl_attack, aes(x = YEAR, y = total_intlfunding, size = Harassment)) + # size indicates the bubble plot 
  geom_point() + #the size will map onto the point graph 
  labs(x = "Year", y = "Number of Countries with Restrcitions") +
  ggtitle("Total Countries with International Funding Restrictions \n and Systematic Harassment of NGOs") +
  scale_size(name="Number of Countries with Harassment") + #for the bubble plot legend
  ylim(0, 30) +
  theme_economist() +
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) + 
  geom_vline(xintercept = 2003, color = "red") #Color Revolution

# Save plot for uploading to the Github 
ggsave("initialdataset_intlfunding_harassment.png")

```

