---
title: "Analyzing and Visualizing Other Explanatory Variables with Initial Dataset"
author: "Jennie Barker"
date: "5/3/2020"
output: html_document
---
## Part 3: In this script, I get to the main part of my analysis, in which I examine the relationship between the international funding restrictions in the Bakke et all dataset and 1.) requests for election assistance (von Borzykowski) 2.) civil society participation (V-Dem) and 3.) public opinion of the U.S. and China (Gallup)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Load Packages
```{r}
# Remove all objects
rm(list=ls())

# Unload all packages 
library(pacman)
pacman::p_unload(all)

# Add packages 
pacman::p_load(
  tidyverse, 
  data.table,  
  foreign, 
  magrittr, 
  skimr, 
  readxl,
  ggthemes,
  writexl
)
```
## 2. Set Working Directory 

```{r}
setwd("~/Documents/Comp Tools - Spring 2020/Final Project ")
getwd()
```
## 3. Is there a relationship between requesting technical election assistance and international funding restrictions? 

# Load and subset initial and new datasets 
```{r}
# Load Initial Dataset 
restrictions_new <- read.csv("restrictions_new.csv")

# Load Election Assistance Dataset 
load("Borzyskowski2016.Rdata")
election_assistance_raw <- table

#Save to upload to the Github 
write.csv(election_assistance_raw, "election_assistance_raw.csv")

#The data does not easily present itself for merging with the initial restrictions dataset, as it only includes election years rather than all years. For this dataset, I will just do some simple plots. 

#Subset to only get relevant columns 
election_assistance_new <- select(election_assistance_raw, CountryName, year, RequestTechElAsst_UN, RequestObservers)

write.csv(election_assistance_new, file="election_assistance_new.csv")
```

# Building the Dataframe 

```{r}
# Frequency of elections by country 
elec_frequency <- election_assistance_new %>%
  count(CountryName) %>%
  group_by(CountryName)
```

```{r}
# Sum of total requests by country 
total_requests <- election_assistance_new %>%
  group_by(CountryName) %>%
  summarise(TechAssistance = sum(RequestTechElAsst_UN, na.rm = T), Observers = sum(RequestObservers, na.rm = T))
```

```{r}
# Add columns together 
total_requests_election <- total_requests %>% 
  add_column(ElecFrequency = elec_frequency$n)

# Add columns with proportion of election years with requests for tech assistance and observers to ease comparison in visualizations 
total_requests_election_prop <- total_requests_election %>%
  mutate(ProportionTech = TechAssistance / ElecFrequency) %>% #mutate to incorporate proportion 
  mutate(ProportionObserver = Observers / ElecFrequency)
```

```{r} 
#Now I want to check how many names overlap in the initial restrictions dataset and the election assistance dataset:

# Get countries that had restrictions on international funding (n = 49)
intlfunding_countries <- restrictions_new %>%
  group_by(COUNTRY) %>%
  filter(sum(FUNDING_INT) >= 1)

# Sum of yearly total by country 
intlfunding_country_names <- intlfunding_countries %>%
  group_by(COUNTRY) %>%
  summarise(International_Restriction = sum(FUNDING_INT, na.rm = T))

# Check overlap 
shared_country_names <- intlfunding_country_names[intlfunding_country_names$COUNTRY %in% total_requests_election$CountryName,]
print(shared_country_names)

# There are only 39 countries that overlap (plus Cote d'Ivoire and Serbia--something funny appears to be happening because of the ', so there are 41 countries that overlap). This is likely because some countries included in the restrictions dataset may not hold elections (China, Saudi Arabia, UAE, Vietnam, and Eritrea are examples).
```

```{r}
#Now I will subset the elections frequency dataset to only include the countries that are in the international funding restrictions dataset, which will help me merge the dataset. 

total_requests_election_subsetted <- filter(total_requests_election_prop, CountryName %in% c("Algeria", "Armenia", "Azerbaijan", "Bangladesh", "Belarus", "Cote d’Ivoire", "Egypt", "Equatorial Guinea", "Ethiopia", "Fiji", "Hungary", "India", "Indonesia", "Iran", "Iraq", "Israel", "Jordan", "Kazakhstan", "Kuwait", "Kyrgyz Republic", "Malaysia", "Nicaragua", "North Korea", "Oman", "Peru", "Russia", "Rwanda", "Singapore", "Serbia (Yugoslavia)", "Slovakia", "Sri Lanka", "Sudan", "Syria", "Togo", "Tunisia", "Turkey", "Ukraine", "Uzbekistan", "Venezuela", "Yemen", "Zimbabwe"))
```

```{r}
# Now I want to add the column with the total number of restrictions from the other dataset to the election assistance dataset 

# Removing countries that do not match in the subsetted initial dataset
intlfunding_countries_subsetted <- filter(intlfunding_country_names, !COUNTRY %in% c("Barbados", "China", "Eritrea", "Saudi Arabia", "South Sudan", "United Arab Emirates", "Vietnam"))

# Rename two entries in the election dataset 
total_requests_election_subsetted$CountryName <- sub("Cote d’Ivoire", "Cote d'Ivoire", total_requests_election_subsetted$CountryName)

total_requests_election_subsetted$CountryName <- sub("Serbia (Yugoslavia)", "Serbia", total_requests_election_subsetted$CountryName)

# Because I struggled with the Serbia entry in this dataset, I'll just change it in the other one. 

intlfunding_countries_subsetted$COUNTRY <- sub("Serbia", "Serbia (Yugoslavia)", intlfunding_countries_subsetted$COUNTRY)

```

```{r}
# Now, I am going to combine these two datasets 

df1 <- total_requests_election_subsetted %>% 
  add_column(IntlFundingRestriction = intlfunding_countries_subsetted$International_Restriction) 

# Add a column with proportional value of international funding restrictions so that it matches the proportion of election years
df1<- df1 %>%
  mutate(IntlFundingProp = IntlFundingRestriction / 20)

View(df1)
  
```

```{r}
# This data frame likely requires more mutation for the best visualization. 

# Turn proportional variables into four-tiered categorical variables
df2 <- df1 %<>%
  mutate(ProportionTech = ifelse(ProportionTech >= 0.6666666, "3", ifelse(ProportionTech >= 0.3333333, "2", ifelse(ProportionTech > 0, "1", "0"))))

df2 <- df1 %>%
mutate(ProportionObserver = ifelse(ProportionObserver >= 0.6666666, "3", ifelse(ProportionObserver >= 0.3333333, "2", ifelse(ProportionObserver > 0, "1", "0"))))

# Ensure that the columns are factor

df2$ProportionTech <- as.factor(df2$ProportionTech)
df2$ProportionObserver <- as.factor(df2$ProportionObserver)

#Save to upload to the Github 
write.csv(df2, file = "restrictions_assistance.csv")

```

# Visualize: countries with international funding restrictions and requests for election assistance 

```{r}
#Finally, we can visualize this! 

ggplot(df2, aes(x = reorder(CountryName, IntlFundingRestriction), y = IntlFundingRestriction, fill = ProportionTech)) + #will change the bar graph colors to match the values in ProportionTech
  geom_bar(stat = "identity") +
  labs(x = "Country", y = "Total Number of Yrs", fill = "% of Election Years with Requests") + #labels 
  ggtitle("Total Number of Years with International Funding \n Restrictions and Proportion of Years with \n Requests for Assistance") +
    theme_economist()+ 
    theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5, size = 8,  margin=margin(-20,0,0,0)), legend.text = element_text(size = 7), plot.title = element_text(hjust = 0.5)) + #make font size smaller for legend text 
  scale_fill_discrete(labels = c("None", "0 - 33%", "33 - 66%", "Up to 100%")) #label legend

# Save plot to upload to Github 
ggsave("funding_electionassistance.png")
```
# Visualize: countries with international funding restrictions and requests for election observers 
```{r}
# How does this look for proportion of requests for observers? 

ggplot(df2, aes(x = reorder(CountryName, IntlFundingRestriction), y = IntlFundingRestriction, fill = ProportionObserver)) + #will change the bar graph colors to match the values in ProportionObserver
  geom_bar(stat = "identity") +
  labs(x = "Country", y = "Total Number of Yrs", fill = "% of Election Years with Requests") + #labels 
  ggtitle("Total Number of Years with International Funding \n Restrictions and Proportion of Years with \n Requests for Observers") +
    theme_economist()+ 
    theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5, size = 8,  margin=margin(-20,0,0,0)), legend.text = element_text(size = 7), plot.title = element_text(hjust = 0.5)) + #make font size smaller for legend text 
  scale_fill_discrete(labels = c("None", "0 - 33%", "33 - 66%", "Up to 100%")) #label legend

# Save plot to upload to Github 
ggsave("funding_electionobservers.png")
```
## 4. What is the relationship between civil society participation and international funding restrictions? 

# The first step is to download VDEM data on Civil Society Participation 

```{r}
vdem <- readRDS("V-Dem-CY-Core-v10.rds")

# There is an incredible amount of data here. I will begin subsetting it. 

# Only get Civil Society Participation Index Score, along with country name and year
vdem_subsetted <- select(vdem, country_name, year, v2x_cspart)

# Get rid of years that I do not need (I will match it with Bakke et al: 1994-2014)

vdem_subsetted <-filter(vdem_subsetted, year %in% c(1994, 1995, 1996, 1997, 1998, 1999, 2000, 2001, 2002, 2003, 2004, 2005, 2006, 2007, 2008, 2009, 2010, 2011, 2012, 2013, 2014))

# Get rid of donor countries to match Bakke et al. 

vdem_subsetted <- filter(vdem_subsetted, !country_name %in% c("Australia", "Austria", "Belgium", "Canada", "Denmark", "Finland", "France", "Germany", "Greece", "Iceland", "Ireland", "Italy", "Japan", "Korea, Republic of", "Luxembourg", "Netherlands", "New Zealand", "Norway", "Portugal", "Spain", "Sweden", "Switzerland", "Taiwan", "United Kingdom", "United States of America"))

# Save as csv to upload to the github 

write.csv(vdem_subsetted, file = "vdem_subsetted.csv")

# Subset Bakke et al as well

restrictions_subsetted <- select(restrictions_new, COUNTRY, YEAR, FUNDING_INT)
```

# Prepare to merge 
```{r}
# Check overlap
shared_country_names1 <- restrictions_subsetted[restrictions_subsetted$COUNTRY %in% vdem_subsetted$country_name,]
print(shared_country_names1)

# There isn't perfect overlap here...only 2819 observations of 3111 and 3216 overlap here. This is likely because of names of countries, as well as countries not included. I will have to further subset the datasets so they match. 
```

```{r}
# I need to fix a few manual errors (missing years especially), which I will do in Excel 

# Not run - will overwrite Excel files 
#write_xlsx(x = restrictions_subsetted, path = "restrictions_subsetted.xlsx", col_names = TRUE)

# Not run 
#write_xlsx(x = vdem_subsetted, path = "vdem_subsetted.xlsx", col_names = TRUE)
```

```{r}
# Now I will reload the data 

vdem_subsetted_1 <- read_excel("vdem_subsetted.xlsx")
restrictions_subsetted_1 <- read_excel("restrictions_subsetted.xlsx")

# Now I will save these as csv files to upload to the Github 

write.csv(vdem_subsetted_1, file = "vdem_subsetted_1.csv")
write.csv(restrictions_subsetted_1, file = "restrictions_subsetted_1")
```

## Combining the Datasets
```{r}
# Now I will merge the datasets using the inner_join function (which merges based on the two shared columns)
total <- inner_join(vdem_subsetted_1, restrictions_subsetted_1)

xtabs(~FUNDING_INT, data = total)

# We can see that there are 239 observations of restrictions and 2768 with no observations 
```


## Visualize data 
```{r}
# Now I can visualize the data. I want to start with comparing the average civil society partcipation during restriction years and non-restriction years 

viz1 <- total %>%
  group_by(FUNDING_INT) %>%
  summarise(mean_value = mean(v2x_cspart)) # average value of all countries

ggplot(viz1, aes(x = FUNDING_INT, y= mean_value)) + 
  geom_bar(stat = "identity", width = 0.5, fill = "deepskyblue") + #bar graph
  labs(x = "Country-Year Observations", y = "Mean Index Score") + #labels 
  ggtitle("Civil Society Participation Index \nDuring Restriction and Non-Restriction Years \n for all Recipient Countries") +
    theme_economist() +
  ylim(0, 1) +
  scale_x_discrete(limits=c(0, 1)) + #scale bar graph 
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) 

# Save image to Github 

ggsave("funding_civlsociety.png")

```

```{r} 
# Now by year 
viz2 <- total %>%
  group_by(FUNDING_INT, YEAR) %>%
  summarise(mean_value = mean(v2x_cspart))

ggplot(viz2, aes(x = YEAR, y= mean_value, fill = factor(FUNDING_INT))) + #factor so FUNDING_INT is read as categorical 
  geom_bar(stat = "identity", position = "dodge") + # so that they aren't stacked but are side by side 
  labs(x = "Year", y = "Mean Index Score", fill = "Restriction") +
  ggtitle("Civil Society Participation Index by Year /n for all Recipient Countries") +
    theme_economist() +
  ylim(0, 1) + 
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) 

# Save image to Github 

ggsave("funding_civlsociety_byyear.png")
```

```{r}
# Next, I want to make a visualization based on a logit regression of the data 

logit <- glm(formula = FUNDING_INT ~ v2x_cspart, family = "binomial", data = total)

coef1 <- broom::tidy(logit, conf.int = TRUE) %>% print()

#Using Julia's sample code 
coef1 %>% 
  filter(term != "(Intercept)") %>%
  ggplot(aes(x = term, y = estimate)) +
  geom_point() +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
  geom_hline(aes(yintercept = 0), colour = "#990000", linetype = "dashed") + 
  labs(title = "Coefficients of logit regression model") +
  ylab(NULL) + xlab(NULL) +
  theme_economist()

## Because of the sparcity of the dataset that I used, this may be why this looks the way it does. Either way, it was good practice to see how I might generate this type of plot when I have a better statistical background. 

ggsave("funding_civlsociety_coefficients.png")

```

## 5. How do countries that have implemented restrictions view the US?

## Get the data and subset it 

```{r}
# Load raw Gallup data on worldwide public opinion on U.S. leadership 
gallup_us <- read_excel("Gallup_USLeadership.xlsx")

View(gallup_us)

# Remove donor country observations and subset to include only years 2009-2014, which have the most consistent observations for most countries 

#Select countries 
gallup_us_subsetted <- filter(gallup_us, !Country %in% c("Australia", "Austria", "Belgium", "Canada", "Denmark", "Finland", "France", "Germany", "Greece", "Iceland", "Ireland", "Italy", "Japan", "South Korea", "Luxembourg", "Netherlands", "New Zealand", "Norway", "Portugal", "Spain", "Sweden", "Switzerland", "Taiwan", "United Kingdom"))

#Select years 
gallup_us_subsetted <-filter(gallup_us_subsetted, Year %in% c(2009, 2010, 2011, 2012, 2013, 2014))

# Save to upload to the Github 
write.csv(gallup_us_subsetted, file = "gallup_us_subsetted.csv")
```

```{r}
# Subset restrictions dataset to include only those same yearly observations 

restrictions_subsetted_gallup <- filter(restrictions_subsetted, YEAR %in% c(2009, 2010, 2011, 2012, 2013, 2014))

#There are over 200 observations that are different between the two datasets. Because this is likely due to missing yearly observations, I will manually fix it. 

#Not run
# write_xlsx(x = restrictions_subsetted_gallup, path = "restrictions_subsetted_gallup.xlsx", col_names = TRUE)

# Not run 
#write_xlsx(x = gallup_us_subsetted, path = "gallup_us_subsetted.xlsx", col_names = TRUE)

```

## Join dataframes 

```{r}
# Re-add data 
gallup_us_subsetted1 <- read_excel("gallup_us_subsetted.xlsx")
restrictions_subsetted_gallup_us <- read_excel("restrictions_subsetted_gallup.xlsx")

# Join datasets 

# Mutate Year column within gallup dataframe so it matches the other 
gallup_us_subsetted1 <- gallup_us_subsetted1 %>% mutate(Year = as.numeric(Year))

#Merge datasets using inner_join function 
total1 <- inner_join(gallup_us_subsetted1, restrictions_subsetted_gallup_us)

xtabs(~FUNDING_INT, data = total1)
```

## Visualize data 

```{r}
# Approval of US Leadership - Grouped 
viz3 <- total1 %>%
  group_by(FUNDING_INT) %>%
  summarise(mean_value = mean(Approve)) #mean value of approval 

ggplot(viz3, aes(x = FUNDING_INT, y= mean_value)) + 
  geom_bar(stat = "identity", width = 0.5, fill = "red4") + #bar graph 
  labs(x = "Country-Year Observations", y = "Mean Approval of US Leadership") +
  ggtitle("Mean Approval of US Leadership \nDuring Restriction and Non-Restriction Years") +
    theme_economist() +
  ylim(0, 1) +
  scale_x_discrete(limits=c(0, 1)) + 
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) 

ggsave("funding_usapproval_total.png")

```

```{r}
# Approval of US Leadership - By Year 

viz4 <- total1 %>%
  group_by(FUNDING_INT, Year) %>%
  summarise(mean_value = mean(Approve))

ggplot(viz4, aes(x = Year, y= mean_value, fill = factor(FUNDING_INT))) + #factor so FUNDING_INT is read as categorical 
  geom_bar(stat = "identity", position = "dodge") + # so that they aren't stacked but are side by side 
  labs(x = "Year", y = "Mean Approval of US Leadership", fill = "Restriction") + ggtitle("Approval of US Leadership by Year") +
    theme_economist() +
  ylim(0, 1) + 
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(values = c("#3366FF", "#006600"))

# Save plot to upload to Github 
ggsave("funding_usapproval_year.png")
```

## 6. How do countries that have implemented restrictions view China?

# Load data 
```{r}
gallup_china <- read_excel("Gallup_ChinaLeadership.xlsx")

View(gallup_china)

# Remove donor country observations and subset to include only years 2009-2014, which have the most consistent observations for most countries 

gallup_china_subsetted <- filter(gallup_china, !Country %in% c("Australia", "Austria", "Belgium", "Canada", "Denmark", "Finland", "France", "Germany", "Greece", "Iceland", "Ireland", "Italy", "Japan", "South Korea", "Luxembourg", "Netherlands", "New Zealand", "Norway", "Portugal", "Spain", "Sweden", "Switzerland", "Taiwan", "United Kingdom", "United States of America"))

gallup_china_subsetted <-filter(gallup_china_subsetted, Year %in% c(2009, 2010, 2011, 2012, 2013, 2014))

#Save as CSV to upload to Github 
write.csv(gallup_china_subsetted, file = "gallup_china_subsetted.csv")
```

```{r}
# Check overlap 

shared_country_names <- restrictions_subsetted_gallup_us[restrictions_subsetted_gallup_us$Country %in% gallup_china_subsetted$Country,]
print(shared_country_names)

# There are a few observations that do not overlap. I will edit it and reload it back into R. 

#Not run
#write_xlsx(x = gallup_china_subsetted, path = "gallup_china_subsetted.xlsx", col_names = TRUE)
```

# Join dataframes 

```{r}
# Reload data 
gallup_china_subsetted <- read_excel("gallup_china_subsetted.xlsx")
restrictions_subsetted_gallup_china <- read_excel("restrictions_subsetted_gallup_china.xlsx")

# Make sure the year column from the gallup data is of the same class 
gallup_china_subsetted <- gallup_china_subsetted %>% mutate(Year = as.numeric(Year))

#Merge datasets using join function 
total2 <- inner_join(gallup_china_subsetted, restrictions_subsetted_gallup_china)
```

## Visualize data 

```{r}
# Approval of China's Leadership - Grouped 
viz5 <- total2 %>%
  group_by(FUNDING_INT) %>%
  summarise(mean_value = mean(Approve))

ggplot(viz5, aes(x = FUNDING_INT, y= mean_value)) + 
  geom_bar(stat = "identity", width = 0.5, fill = "red4") +
  labs(x = "Country-Year Observations", y = "Mean Approval of China's Leadership") +
  ggtitle("Mean Approval of China's Leadership \nDuring Restriction and Non-Restriction Years") +
    theme_economist() +
  ylim(0, 1) +
  scale_x_discrete(limits=c(0, 1)) + #organize bars 
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) 

# Save to upload to Github 
ggsave("funding_chinaapproval_total.png")

```

```{r}
# Approval of China's Leadership - By Year 

viz6 <- total2 %>%
  group_by(FUNDING_INT, Year) %>%
  summarise(mean_value = mean(Approve))

ggplot(viz6, aes(x = Year, y= mean_value, fill = factor(FUNDING_INT))) + #factor so FUNDING_INT is read as categorical 
  geom_bar(stat = "identity", position = "dodge") + # so that they aren't stacked but are side by side 
  labs(x = "Year", y = "Mean Approval of China's Leadership", fill = "Restriction") + ggtitle("Approval of China's Leadership by Year") +
    theme_economist() +
  ylim(0, 1) + 
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(values = c("#3366FF", "#006600"))

#Save plot to upload to Github 
ggsave("funding_chinaapproval_year.png")

```

## Do disapproval rates differ? 
```{r}
# US Disapproval 

viz7 <- total1 %>%
  group_by(FUNDING_INT, Year) %>%
  summarise(mean_value = mean(Disapprove))

ggplot(viz4, aes(x = Year, y= mean_value, fill = factor(FUNDING_INT))) + #factor so FUNDING_INT is read as categorical 
  geom_bar(stat = "identity", position = "dodge") + # so that they aren't stacked but are side by side 
  labs(x = "Year", y = "Mean Disapproval of US Leadership", fill = "Restriction") + ggtitle("Disapproval of US Leadership by Year") +
    theme_economist() +
  ylim(0, 1) + 
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(values = c("#9966CC", "#66CCCC"))

#Save to upload to Github 
ggsave("funding_usdisapproval_year.png")
```

```{r}
viz8 <- total2 %>%
  group_by(FUNDING_INT, Year) %>%
  summarise(mean_value = mean(Disapprove))

ggplot(viz4, aes(x = Year, y= mean_value, fill = factor(FUNDING_INT))) + #factor so FUNDING_INT is read as categorical 
  geom_bar(stat = "identity", position = "dodge") + # so that they aren't stacked but are side by side 
  labs(x = "Year", y = "Mean Disapproval of China's Leadership", fill = "Restriction") + ggtitle("Disapproval of China's Leadership by Year") +
    theme_economist() +
  ylim(0, 1) + 
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) +
  scale_fill_manual(values = c("#FFFF66", "#99CCFF"))

# Save to upload to Github 
ggsave("funding_chinadisapproval_year.png")
```

## 7. Trust in NGOs or Charitable Organizations 

# My final analysis is the levels of trust in NGOs in countries that have implemented restrictions versus those that have not. This survey was only conducted in 2018, so I will simply add a column in the Gallup dataset of whether or not the country experienced a restriction at some point in between 1994-2014. This is based on the list of countries generated in my comparison of Bakke et al (2020). and Dupuy et al. (2016) 

# Load data 
```{r}
gallup_ngos <- read_excel("Gallup_NGOs.xlsx")

# Remove donor countries 
gallup_ngos <- filter(gallup_ngos, !Country %in% c("Australia", "Austria", "Belgium", "Canada", "Denmark", "Finland", "France", "Germany", "Greece", "Iceland", "Ireland", "Italy", "Japan", "South Korea", "Luxembourg", "Netherlands", "New Zealand", "Norway", "Portugal", "Spain", "Sweden", "Switzerland", "Taiwan", "United Kingdom", "United States of America"))

```

# Visualize data 

```{r}
# Grouped 
viz9 <- gallup_ngos %>%
  group_by(Restriction) %>%
  summarise(mean_value = mean(Yes))

ggplot(viz9, aes(x = Restriction, y= mean_value)) + 
  geom_bar(stat = "identity", width = 0.5, fill = "blue") + 
  labs(x = "Restriction", y = "Mean Trust in NGOs and Charitable Orgs") + ggtitle("Mean Trust in NGOs and Charitable Organizations") +
    theme_economist() +
  ylim(0, 1) + 
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(limits=c(0, 1)) 

#Save to upload to Github 
ggsave("funding_NGOtrust.png")
```

```{r} 
# How does mean approval vary among countries with restrictions? 

#Subset to only include countries in the original Bakke et al dataset 
gallup_ngos_subset <- filter(gallup_ngos, Country%in% c("Algeria", "Armenia", "Azerbaijan", "Bangladesh", "Belarus", "Cote d'Ivoire", "Egypt", "Equatorial Guinea", "Ethiopia", "Fiji", "Hungary", "India", "Indonesia", "Iran", "Iraq", "Israel", "Jordan", "Kazakhstan", "Kuwait", "Kyrgyz Republic", "Malaysia", "Nicaragua", "North Korea", "Oman", "Peru", "Russia", "Rwanda", "Singapore", "Serbia", "Slovakia", "Sri Lanka", "Sudan", "Syria", "Togo", "Tunisia", "Turkey", "Ukraine", "Uzbekistan", "Venezuela", "Yemen", "Zimbabwe"))

ggplot(gallup_ngos_subset, aes(x = Country, y= Yes)) + 
  geom_bar(stat = "identity", width = 0.5) + 
  labs(y = "Mean Trust in NGOs and Charitable Orgs") + ggtitle("Mean Trust in NGOs and Charitable Organization \n by Country with Restriction") +
    theme_economist() +
  ylim(0, 0.8) +
  theme(text = element_text(family = "Arial"), plot.title = element_text(hjust = 0.5)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5, size = 8,  margin=margin(-15,0,0,0))) + 
   xlab(NULL)

ggsave("funding_NGOtrust_bycountry.png")
```
